### 2014-06-10 analysis/network_properties.Rmd
network properties fixed

```{r}
#Collect the network data and create a data table to hold the network properties
props <- NULL
num_networks <- c(1,2,3,4,5)
k_values <- seq(10,50,10) 
runs <- sort(unique(network_data[,"run"]))

require(BBmisc)#for progress bar
pb <- makeProgressBar(min=0, max=(length(num_networks)*length(k_values)*length(runs)), label="network analysis")

  #pre-alocate a matrix for the network properties
  props <- matrix(nrow=(length(num_networks)*length(k_values)*length(runs))-1, ncol=7)
  i <- 1

for(n in num_networks){
  #reads the properties for all the k-regular networks with the given k and num_networks

  for(k in k_values){
    cfg <- params[params$"num.network" == n & params$"network.0.k" == k,][[1]]
    for(r in runs){

        fn_net <- mwhich(x=network_data, cols=c("run","cfg.id"), vals=list(r,cfg),comps=list("eq"))
        f_network_data <- network_data[fn_net,c("node1","node2")]
        network <- read.network(ndata=f_network_data)

        network$properties <- cbind(k,n,r,measure.network(network))
        colnames(network$properties)[1:3] <- c("k","networks","run")

        #append the properties to the current matrix
        props[i,] <- network$properties
        i <- i + 1

        #some progress feddback
        pb$inc(1,paste("reading n=",n,"k=",k,"and run=",r,"\n"))
    }
    gc()
  } 
}
pb$kill()

colnames(props) <- colnames(network$properties)

>>>>

```{r}
#Collect the network data and create a data table to hold the network properties
require(parallel)

## Number of workers (R processes) to use:
numWorkers <- 8

measure_parallel <- function(cfg,r){
  data <- network_data
  network <- read.big.network(data,cfg,r)
  properties <- measure.network(network)
  properties <- cbind(r,properties)
  return(properties)
}

props <- NULL
num_networks <- c(1,2,3,4,5)
k_values <- c(1:5,seq(10,50,10))
runs <- sort(unique(network_data[,"run"]))

require(BBmisc)#for progress bar
pb <- makeProgressBar(min=0, max=(length(num_networks)*length(k_values)), label="network analysis")

#pre-alocate a matrix for the network properties
props <- matrix(nrow=(length(num_networks)*length(k_values)*length(runs)), ncol=7)
i <- 0

for(n in num_networks){
  #reads the properties for all the k-regular networks with the given k and num_networks 
  for(k in k_values){
    cfg <- params[params$"num.network" == n & params$"network.0.k" == k,][[1]]

    properties <- mcmapply(cfg=cfg, r=runs, measure_parallel, mc.cores = numWorkers)
    properties <- t(properties)

    props[(i+1):(i+100),] <- cbind(k,n,properties)
    i <- i + 100  
    #some progress feddback
    pb$inc(1,paste("reading n=",n,"k=",k,"\n"))
    gc()
  } 
}
pb$kill()

colnames(props)<-c("k","networks","run","nodes","edges","clustering-coefficient","average-path-length")
